Learning how to act: making good decisions with machine learning

### 2017-09-28 thesis/offcuts_chapter6.tex
adds section for bob, starting work on talk

@@

\item Write a talk - include slide on causal inference without do
\item Check what I actually have to do to submit
\item Add something about Granger causality - does this belong in chapter 2 or chapter 3?
\item Sell my PhD as two key contribution. 1) A technical one, the other educational and unifying (across viewpoints)
\item Add a chapter in 'PhD prose' making some statement about the intersection of prediction and causality. When is a problem causal, what bounds does predictive accuracy give on causal models? To what degree is predictive accuracy a metric on which causal models can be judged? 
\item Benchmark estimation algorithms
\item clarify causal interpretation of Dirichlet models
\item Empirical evaluation of bandit algorithms (updated to include latest suggestions). Maybe a proper software bench marking solution?
\item If comparing bandit performance, it would be interesting to include some that violate the stochastic bandit assumption. For example, if the rewards change slowly over time or jump suddenly a limited number of times, or with some small probability. 
\item Does defining causality in term of the truncated product formula ensure that a causal Bayesian network is unique? It would seem no, one can ad links (although this is hardly useful) - seems like there is no reverse condition. 
\item Statistisian/Econometricians and computer science seem to use different definitions of optimality (bandits vs efficient estimators). Clarify this - would make a good blog post I think. 
\end{enumerate}

@@

>>>>

Note that in the general case, where the interventional distributions over the parents of $Y$, the effect of a given intervention by be non-identifiable even with good overlap and thus it is not possible to infer ahead of time the extent to which estimation is biased via confounding and thus the relative value of observational versus interventional data.

@@

\item Write a talk - include slide on causal inference without do
\item Check what I actually have to do to submit
\item Add something about Granger causality - does this belong in chapter 2 or chapter 3?
\item  When is a problem causal, what bounds does predictive accuracy give on causal models? To what degree is predictive accuracy a metric on which causal models can be judged? 
\item Benchmark estimation algorithms
\item clarify causal interpretation of Dirichlet models
\item Empirical evaluation of bandit algorithms (updated to include latest suggestions). Maybe a proper software bench marking solution?
\item If comparing bandit performance, it would be interesting to include some that violate the stochastic bandit assumption. For example, if the rewards change slowly over time or jump suddenly a limited number of times, or with some small probability. 
\item Does defining causality in term of the truncated product formula ensure that a causal Bayesian network is unique? It would seem no, one can ad links (although this is hardly useful) - seems like there is no reverse condition. 
\item Statistisian/Econometricians and computer science seem to use different definitions of optimality (bandits vs efficient estimators). Clarify this - would make a good blog post I think. 
\end{enumerate}

@@

In addition, the parametric structural equation models favoured in economics can be extended to analyse cyclic (otherwise referred to as non-recursive) models.

### 2017-09-28 thesis/recipe_for_causal_inference.tex
adds section for bob, starting work on talk

\usepackage[latin1]{inputenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\begin{document}
\pagestyle{empty}

% Define block styles
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
    text width=10em, text centered, rounded corners, minimum height=3em]
\tikzstyle{line} = [draw, -latex']

\begin{tikzpicture}[node distance = 2cm, auto]
    % Place nodes
    \node [block] (drawgraph) {Use prior knowledge to draw the graph};
    \node [block, below of=drawgraph] (docalc) {Apply the Do Calculus};
    \node [block, below left of=docalc,node distance=3.5cm] (fail) {Non Identifiable};
    \node [block, below right of=docalc, node distance=3.5cm] (success) {Identifiable};
    \node [block, below of=fail](notident){Bugger! You will have to make additional assumptions or do experiments};
     \node [block, below of=success](ident){Great! Apply the formula from the do-caclulus to estimate effect.};
     \node [block, fill=red!10, dashed, right of=ident,node distance=4.5cm](stats){Deal with pesky statistical issues introduced by finite data as you see fit};

>>>>

\usepackage[latin1]{inputenc}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{xcolor}

\definecolor{talk}{HTML}{729FCF}
\definecolor{talk2}{HTML}{E8A753}
\begin{document}
\pagestyle{empty}

% Define block styles
\tikzstyle{block} = [rectangle, draw, fill=talk!50, 
    text width=10em, text centered, rounded corners, minimum height=3em]
\tikzstyle{line} = [draw, -latex']

\begin{tikzpicture}[node distance = 2cm, auto]
    % Place nodes
    \node [block] (drawgraph) {Use prior knowledge to draw the graph};
    \node [block, below of=drawgraph] (docalc) {Apply the Do Calculus};
    \node [block, below left of=docalc,node distance=3.5cm] (fail) {Non Identifiable};
    \node [block, below right of=docalc, node distance=3.5cm] (success) {Identifiable};
    \node [block, below of=fail](notident){Bugger! You will have to make additional assumptions or do experiments};
     \node [block, below of=success](ident){Great! Apply the formula from the do-caclulus to estimate effect.};
     \node [block, fill=talk2!50, dashed, right of=ident,node distance=4.5cm](stats){Deal with pesky statistical issues introduced by finite data as you see fit};
